Model Finding for Recursive Functions in SMT\thanks{ This research is partially supported by the Inria technological development action ``Contre-exemples Utilisables par Isabelle et Coq'' (CUIC). }

### 2015-05-07 tex/main.tex
Change Leon reference.

Our empirical evaluation on benchmarks from the IsaPlanner proof planner~\cite{DBLP:conf/itp/JohanssonDB10}
and the Leon verifier~\cite{suter-et-al-2011} provides
evidence that this translation improves the effectiveness of the SMT solvers
\cvc and \ziii for finding counterexamples to verification conditions
(Section~\ref{sec:evaluation}). The approach is implemented as a preprocessor
in \cvc (Section~\ref{sec:front-end}). When invoked with a
command-line option, the solver assumes that functions introduced using the
\texttt{define-fun-rec} command are admissible and translates them accordingly.

@@

The Leon system \cite{suter-et-al-2011} implements a procedure that can both
produces proofs and counterexamples for properties of terminating functions
written in a subset of Scala. Leon is based on an SMT solver. It avoids
quantifiers altogether by unfolding recursive definitions up to a certain
depth, which is increased iteratively as necessary.
The approach described in this paper works in an analagous manner, 
where instead the SMT solver is invoked only once 
and where quantifier instantiation amounts to function unfolding.
It is worth investigating how existing approaches for algorithms based on function unfolding
can inform approaches for dedicated quantifier instantiation techniques for function definitions,
and vice versa.
%\jb{Andy: Can you add some more here? You're the Leon pro! E.g. why/when do we think
%that our approach might be better?}
%\ct{About Leon, the reviewers and readers may wonder why we do not do the same, that is, just progressively unfold the recursive definitions until a model is found.
%We should probably say something in this regard.
%}
% It is not a question of "should you instead unfold function definitions?" since that's essential what quantifier instantiation does.  
% The question is "is quantifier instantiation a good way of unfolding function definitions?" 
% or "how can we instrument quantifier instantiation to mimic/improve upon existing strategies for function unfolding? --ajr

>>>>

Our empirical evaluation on benchmarks from the IsaPlanner proof planner~\cite{DBLP:conf/itp/JohanssonDB10}
and the Leon verifier~\cite{blanc2013overview} provides
evidence that this translation improves the effectiveness of the SMT solvers
\cvc and \ziii for finding counterexamples to verification conditions
(Section~\ref{sec:evaluation}). The approach is implemented as a preprocessor
in \cvc (Section~\ref{sec:front-end}). When invoked with a
command-line option, the solver assumes that functions introduced using the
\texttt{define-fun-rec} command are admissible and translates them accordingly.

@@

The Leon system~\cite{blanc2013overview} implements a procedure that can both
produces proofs and counterexamples for properties of terminating functions
written in a subset of Scala. Leon is based on an SMT solver. It avoids
quantifiers altogether by unfolding recursive definitions up to a certain
depth, which is increased iteratively as necessary.
The approach described in this paper works in an analagous manner, 
where instead the SMT solver is invoked only once 
and where quantifier instantiation amounts to function unfolding.
It is worth investigating how existing approaches for algorithms based on function unfolding
can inform approaches for dedicated quantifier instantiation techniques for function definitions,
and vice versa.
%\jb{Andy: Can you add some more here? You're the Leon pro! E.g. why/when do we think
%that our approach might be better?}
%\ct{About Leon, the reviewers and readers may wonder why we do not do the same, that is, just progressively unfold the recursive definitions until a model is found.
%We should probably say something in this regard.
%}
% It is not a question of "should you instead unfold function definitions?" since that's essential what quantifier instantiation does.  
% The question is "is quantifier instantiation a good way of unfolding function definitions?" 
% or "how can we instrument quantifier instantiation to mimic/improve upon existing strategies for function unfolding? --ajr
